%-------------------------
% Strata Tech Resume Template
% Architect & author: Ioana-Alexandra Petrache
% License : MIT
%
% This resume template is a heavily customized and architecturally modified
% fork of the called resume (Jake's Resume), framework by Jake Gutierrez, located at 
% (https://github.com/sb2nov/resume).
% Based off of: https://github.com/sb2nov/resume
% Custom modifications include: geometry/layout implementation, PDF compatibility via machine-readable ATS optimizations, design and UI (e.g. fonts, colors), and the (rather) strict typography configurations.

% The UI & some Typographic choice (like the visual aesthetics, some color implementations, and "disruptive" layout choices were heavily inspired by Claud D. Park's legendary [Awesome-CV](https://github.com/posquit0/Awesome-CV) project. 
% ***I always loved the Awesome-CV design but I wanted to build a lighter, single-file LaTeX file that prioritized ATS machine-readability and was more condensed & senior-focused.
%------------------------

\documentclass[letterpaper,10.5pt]{extarticle}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

% Ensuring the generated PDF is machine readable and ATS parsable
\usepackage{cmap} % this should fix the character mapping for various, as the package forces the pdfLaTeX compiler to generate a hardcoded dictionary and embed it directly into the PDF.
\usepackage{iftex}
\ifpdftex
    \input{glyphtounicode} % Loads the glyph-to-unicode dictionary
    \pdfgentounicode=1
\fi

%----------FONT OPTIONS----------
\usepackage[default, light]{roboto}
\usepackage[T1]{fontenc}
%--------------------------------

% Adjust margins, custom:
\usepackage[left=0.5in, top=0.4in, right=0.5in, bottom=0.8in]{geometry}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\definecolor{Minty}{RGB}{12, 130, 97}       % Signature, custom Green
\definecolor{darktext}{RGB}{51, 51, 51}     % For Name and Section Headers
\definecolor{graytext}{RGB}{93, 93, 93}     % For the bullet points custom look
\definecolor{lighttext}{RGB}{153, 153, 153} % For dates and locations (the default, light gray)

% Sections formatting
\titleformat{\section}{
  \nopagebreak\raggedright\Large\bfseries\color{darktext}
}{}{0em}{}[\color{darktext}\titlerule] % This makes the text default to dark grey in the section headers

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {\color{graytext}#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
  \item\small{
    {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{5pt}\item % The command to globally control the spacing between each individual job
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large\color{darktext}#1} & \textit{\small\color{Minty}#4} \\
      {\small\color{graytext}#3} & \textit{\small\color{graytext}#2} \\
    \end{tabular*}\vspace{-1pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small\color{darktext}#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%%%  RESUME START %%%%%%%%


\begin{document}
\color{darktext} % This makes the text default to dark grey for the whole document

%----------HEADING----------
\begin{center}
    {\Huge {\color{graytext}Michelle Sofia-}\textbf{\color{Minty}Gutierrez}} \\ \vspace{5pt}
    {\textcolor{darktext} {Full-Stack Developer | Software Architecture}} \\ \vspace{5pt}
    {\small{\textcolor{darktext}{Barcelona, Spain}}} \\ \vspace{5pt}
    \small \raisebox{-0.1\height}\faPhone\ 34 002 000 000 ~ \href{mailto:michelle.s.gutierrez@example.com}{\raisebox{-0.2\height}\faEnvelope\ \underline{michelle.s.gutierrez@example.com}} ~ 
    \href{https://linkedin.com/in/michelles-gutierrez}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/michelles-gutierrez}}  ~
    \href{https://github.com/msg1654utierrez}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/msg1654utierrez}}
    \vspace{1pt}
\end{center}

%-------------SUMMARY-------------
\section{\textcolor{Minty}{Sum}mary}
\small{\color{graytext}{Senior Full-Stack Developer and Platform Engineer with a focus on building resilient backend services, scalable frontend architectures, and automated CI/CD pipelines. Experienced in bridging the gap between complex client requirements and clean, secure code, while optimizing system performance and engineering smooth development workflows.}}

%-----------EXPERIENCE-----------
\section{\textcolor{Minty}{Exp}erience}
  \resumeSubHeadingListStart

\resumeSubheading
      {Senior Full-Stack Developer}{Jul. 2023 -- Present}
      {Nexus Tech Solutions}{Barcelona, Spain (Hybrid)}
      \resumeItemListStart
        \resumeItem{\textbf{\color{darktext}Architecture \& Scaling}: Architected and developed a high-traffic SaaS dashboard using React and TypeScript, successfully scaling the platform to serve over 50,000 monthly active users.}
        \resumeItem{\textbf{\color{darktext}API Optimization}: Migrated legacy REST APIs to a unified GraphQL endpoint, optimizing database query logic and reducing client-side data fetching time by 40\%.}
        \resumeItem{\textbf{\color{darktext}Pipeline Automation}: Implemented automated integration and unit testing (Jest/Cypress) within GitHub Actions CI/CD pipelines, increasing code coverage to 85\% and reducing critical production bugs.}
      \resumeItemListEnd
      %\vspace{8pt} % Additional line of space, use if needed

    \resumeSubheading
      {Software Developer (Client Solutions)}{May. 2020 -- Feb. 2023}
      {FinTech Partners UK}{\textcolor{Minty}London, UK}
      \resumeItemListStart
        \resumeItem{\textbf{\color{darktext}Customer-Centric Engineering}: Served as the primary technical liaison for enterprise clients, translating complex business requirements into actionable engineering sprints and bespoke software features.}
        \resumeItem{\textbf{\color{darktext}Platform Integration}: Engineered custom API integrations bridging the core application with legacy client systems, reducing onboarding time for new enterprise accounts by 30\%.}
        \resumeItem{\textbf{\color{darktext}User Acceptance Testing (UAT)}: Directed live product demonstrations and UAT sessions, utilizing direct customer feedback to refine front-end UI components and workflows.}
    \resumeItemListEnd
    %\vspace{8pt} % Additional line of space, use if needed

    \resumeSubheading
      {Program Coordinator \& Instructor}{May 2019 -- Apr. 2020}
      {Austin Cinematic Arts Center}{\textcolor{Minty}Austin, TX}
      \resumeItemListStart
        \resumeItem{\textbf{\color{darktext}Event Logistics \& Operations}: Directed scheduling and logistical operations for community film screenings, theatrical performances, and independent arts festivals.}
        \resumeItem{\textbf{\color{darktext}Curriculum Development}: Developed and facilitated educational workshops for local residents, focusing on cinematic history, digital storytelling, and media literacy.}
    \resumeItemListEnd
    %\vspace{8pt}
    
     \resumeSubheading
      {Web Developer (Contract)}{Sept. 2018 -- Apr. 2019}
      {OptimaWeb Solutions}{\textcolor{Minty}Austin, TX}
      \resumeItemListStart
        \resumeItem{\textbf{\color{darktext}Component Development}: Translated UI/UX wireframes into functional, modular React components and managed global state using Redux for a fast-paced EdTech startup.}
        \resumeItem{\textbf{\color{darktext}Cross-Browser Debugging}: Debugged networking and browser-side execution errors, ensuring uniform layout rendering across legacy and modern browsers.}
    \resumeItemListEnd
    %\vspace{8pt} % Additional line of space, use if needed

     \resumeSubheading
      {Junior Web Developer}{Jul. 2017 -- Aug. 2018}
      {Boston Logic}{\textcolor{Minty}Boston, MA}
      \resumeItemListStart
        \resumeItem{\textbf{\color{darktext}Feature Implementation}: Maintained and expanded existing monolithic applications, migrating legacy jQuery interfaces to modern React components.}
        \resumeItem{\textbf{\color{darktext}QA \& Documentation}: Authored comprehensive technical documentation for internal developer onboarding and wrote unit tests for REST endpoints using Jest.}
    \resumeItemListEnd

   \resumeSubheading
      {Software Engineering Intern}{May 2016 -- Aug. 2016}
      {Commonwealth EdTech}{\textcolor{Minty}Boston, MA}
      \resumeItemListStart
        \resumeItem{\textbf{\color{darktext}Feature Development}: Assisted in migrating a legacy jQuery student portal to React.js, improving page load speeds by 25\%.}
        \resumeItem{\textbf{\color{darktext}QA \& Testing}: Wrote comprehensive unit tests using Jest and documented REST API endpoints for the backend engineering team.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  %\vspace{-1pt} % Additional line of space, use if needed

% Page 2 controller for the white space at the top of the second page. This control the space !between main categories!
\newpage
\vspace*{-13pt} % Adjust if needed

%-----------PROFESSIONAL CREDENTIALS AND MODERN STACK EXPOSURE-----------
\section{\textcolor{Minty}{Pro}fessional Credentials \& Modern Stack Exposure}
  \resumeSubHeadingListStart
    
    \resumeProjectHeading
        {\textbf{Backend Engineering \& Service Architecture}}{}
        \vspace{-10pt}
        \resumeItemListStart
            \resumeItem{\textcolor{Minty}{Python}: Production implementation for backend automation \& data pipelines ~ \textbar ~ \textcolor{Minty}{Node.js}: Corporate training \& microservices architecture project ~ \textbar ~ \textcolor{Minty}{Objective-C}: Academic coursework (Boston University) \& legacy mobile support}
        \resumeItemListEnd
        \vspace{-4pt} % Additional line of space, use if needed

    \resumeProjectHeading
        {\textbf{Front-End Systems \& Client Integration}}{}
        \vspace{-10pt}
        \resumeItemListStart
            \resumeItem{\textcolor{Minty}{TypeScript} \& \textcolor{Minty}{JavaScript} (ES6+): Core stack implementation across enterprise client projects ~ \textbar ~ \textcolor{Minty}{React.js}: Advanced component design \& state management optimization ~ \textbar ~ \textcolor{Minty}{Next.js}: Production deployment for high-traffic web applications}
        \resumeItemListEnd
        \vspace{-4pt} % Additional line of space, use if needed
        
      \resumeProjectHeading
        {\textbf{Platform Engineering, Security \& Governance}}{}
        \vspace{-10pt}
        \resumeItemListStart
        \resumeItem{Google Cloud Platform (\textcolor{Minty}{GCP}) \& Cloud Run: Administration \& deployment training ~ \textbar ~ Containerization via \textcolor{Minty}{Docker}: Hands-on pipeline integration ~ \textbar ~ Dedicated training on \textcolor{Minty}{OWASP} secure coding principles (2025) ~ \textbar ~ \textcolor{Minty}{GDPR / ISO 27001}: Compliance framework implementation (2023–-2025)}
        \resumeItemListEnd
        \vspace{-4pt} % Additional line of space, use if needed

      \resumeProjectHeading
        {\textbf{Engineering Workflows \& AI Implementation}}{}
        \vspace{-10pt}
        \resumeItemListStart
          \resumeItem{Introduction to \textcolor{Minty}{Artificial Intelligence and Optimization algorithms} with \textcolor{Minty}{Python} (MIT Online, Professional Cert. - In Progress) ~ \textbar ~ \textcolor{Minty}{Generative AI \& Agentic AI}: Model implementation and logic flows (IBM/Red Hat training, 2025--2026) ~ \textbar ~ \textcolor{Minty}{CI/CD}: GitHub Actions automation project ~ \textbar ~ \textcolor{Minty}{Agile Engineering}: GitFlow workflow standardization (Atlassian Cert., 2024)}
        \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-1pt} % Additional line of space, use if needed
  
%-----------WRITING & PUBLICATIONS-----------
\section{\textcolor{Minty}{Wri}ting \& Publications}
\vspace{4pt}

{\textbf{\color{darktext}Advanced Web Architecture}:} \href{https://example.com}{\color{Minty}GraphQL API Migration} ~ \textbar ~ \href{https://example.com}{\color{Minty}Custom React Hooks}\par
{\small\color{graytext}Authored architectural deep-dives and technical tutorials for premier engineering outlets including The Modern Stack (UK) and Web Engineering Hub.}
\vspace{8pt} % Additional line of space, use if needed

{\textbf{\color{darktext}Modern JavaScript \& UI/UX}:} \href{https://example.com}{\color{Minty}The Component Tree (Personal Blog)}\par
{\small\color{graytext}Authored 50+ articles focused on ES6+ and early React architecture, growing to 15,000 monthly readers before pivoting focus to open-source contributions.}
\vspace{8pt} % Additional line of space, use if needed

{\textbf{\color{darktext}Human-Computer Interaction (HCI)}:} \href{https://example.com}{\color{Minty}Accessibility First: Screen Readers \& Virtual DOM}\par
{\small\color{graytext}Co-authored an academic paper evaluating ARIA labels and semantic HTML performance within complex SPAs for the Boston University department symposium.}
\vspace{4pt} % Additional line of space, use if needed

%-----------EDUCATION---------------
\section{\textcolor{Minty}{Edu}cation \& Linguistic Competencies}
\vspace{4pt}

\textbf{\color{darktext}Artificial Intelligence Algorithms for professionals (with Python)}\par
    {\small\color{graytext}6-month intensive focus on AI, algorithmic logic and neural networks using Python.}
\vspace{6pt} % Additional line of space, use if needed

\textbf{\color{darktext}Bachelor of Arts in Computer Science | Boston University}\par
{\small\color{graytext}Minor in Interactive Design. Coursework focus on data structures, algorithmic logic, and web engineering.}
\vspace{5pt} % Additional line of space, use if needed

\textbf{\color{darktext}Languages}
\vspace{9pt} 
\begin{multicols}{2}
    \begin{itemize}[leftmargin=0.15in, label={\textcolor{graytext}{$\vcenter{\hbox{\tiny$\bullet$}}$}}]
        \item \small{\color{darktext}\textbf{English}: Native Mastery, Academic Specialization}
        \item \small{\color{darktext}\textbf{Spanish}: Full Professional Mastery (C2)}
        \item \small{\color{darktext}\textbf{French}: Operational/Working Proficiency (B1)}
        \item \small{\color{darktext}\textbf{Latin}: Academic Specialization/Basic Proficiency (A2)}
    \end{itemize}
\end{multicols}
%\vspace{4pt} % % Additional line of space, use if needed

    %-----------HOBBIES & INTERESTS---------------
    \section{\textcolor{Minty}{Hob}bies \& Interests}
    {\textcolor{darktext}{\textbf{Cinematic Curation \& Independent Film}:} \color{graytext}Analyzing narrative screenwriting structures and volunteering at independent film festivals.}\par
    {\textcolor{darktext}{\textbf{Marathon Training \& Long-Distance Running}:} \color{graytext}Endurance sports as a practical discipline for cultivating long-term stamina.}\par
    {\textcolor{darktext}{\textbf{Reflective Journaling \& Behavioral Psychology}:} \color{graytext}Studying cognitive patterns and utilizing structured writing for personal retrospectives.}

\end{document}
